\newcommand\rrref{

\begin{thebibliography}{99999999}

\BI{Bal13}{Markus B\"alser}{Fast Matrix Multiplication}{Theory of Computing, Graduate Surveys}{5:1-60, 2013}

\BI{BPR06}{Saugata Basu, Richard Pollack, and Marie-Françoise Roy}{Algorithms in Real Algebraic Geometry}{Springer-Verlag}{2006}

\BI{Bur04}{Peter B\"urgisser}{The Complexity of Factors of Multivariate Polynomials}{Foundations of Computational Mathematics}{4(4):369–396, 2004}

\BI{Can88}{John F. Canny}{Some Algebraic and Geometric Computations in PSPACE}{In Janos Simon, editor, Proceedings of the 20th Annual ACM Symposium on Theory of Computing}{May 2-4, 1988, Chicago, Illinois, USA, pages 460–467. ACM, 1988}

\BI{CLO06}{David A. Cox, John Little, and Donal O’Shea}{Ideals, Varieties, and Algorithms: An Introduction to Computational Algebraic Geometry and Commutative Algebra}{Springer}{2006}

\BI{CW01}{Anthony Carbery and James Wright}{Distributional and $L^q$ norm inequalities for polynomials over convex bodies in $\IR^n$}{Mathematical Research Letters}{8(3):233–248, 2001}

\BI{FS17}{Michael A. Forbes and Amir Shpilka}{A PSPACE Construction of a Hitting Set for the Closure of Small Algebraic Circuits}{}{}

\BI{GMQ16}{Joshua A. Grochow, Ketan D. Mulmuley, and Youming Qiao}{Boundaries of VP and VNP}{In Ioannis Chatzigiannakis, Michael Mitzenmacher, Yuval Rabani, and Davide Sangiorgi, editors, 43rd International Colloquium on Automata, Languages, and Programming}{ICALP 2016, July 11-15, 2016, Rome, Italy, volume 55 of LIPIcs, pages 34:1–34:14 Schloss Dagstuhl - Leibniz-Zentrum fuer Informatik, 2016}

\BI{HS80a}{Joos Heintz and Claus-Peter Schnorr}{Testing Polynomials which Are Easy to Compute(Extended Abstract)}{In Raymond E. Miller, Seymour Ginsburg, Walter A. Burkhard, and Richard J. Lipton, editors, Proceedings of the 12th Annual ACM Symposium on Theory of Computing}{April 28-30, 1980, Los Angeles, California, USA, pages 262–272. ACM, 1980}

\BI{HS80b}{Joos Heintz and Malte Sieveking}{Lower bounds for polynomials with algebraic coefficients}{Theoretical Computer Science}{11(3):321–330, 1980}

\BI{Koi96}{Pascal Koiran}{Hilbert’s Nullstellensatz Is in the Polynomial Hierarchy.}{J. Complexity}{12(4):273–286, 1996}

\BI{LL89}{Thomas Lehmkuhl and Thomas Lickteig}{On the Order of Approximation in Approximative Triadic Decompositions of Tensors}{Theor. Comput. Sci.}{66(1):1–14, 1989}

\BI{Mul17}{Ketan D. Mulmuley}{Geometric complexity theory V: Efficient algorithms for Noether normalization}{J. Amer. Math. Soc.}{30(1):225309, 2017}

\BI{Raz10}{Ran Raz}{Elusive Functions and Lower Bounds for Arithmetic Circuits}{Theory of Computing}{6(1):135–177, 2010}

\BI{San91}{Giovanni Sansone}{Orthogonal Functions}{Dover Books on Advanced Mathematics, Dover Publications}{revised edition, 1991}

\BI{Sha88}{Igor R. Shafarevich}{Basic Algebraic Geometry 2}{Springer-Verlag}{1988}

\BI{SY10}{Amir Shpilka and Amir Yehudayoff}{Arithmetic Circuits: A survey of recent results and open questions}{Foundations and Trends in Theoretical Computer Science}{5(3-4):207–388, 2010}

\BI{Wil74}{Don R. Wilhelmsen}{A Markov inequality in several dimensions}{Journal of Approximation Theory}{11(3):216–220, 1974}

\end{thebibliography}
}
